Stable Hot Spot Analysis (Draft)

### 2017-06-14 paper-main.tex
Added conclusion

Our results are based on the cab taxi data set from New York, Manhattan \cite{TODO}. 
We used only the dataset of January 2016. From that
dataset we used the $pickup_longitude$ and $pickup_latitude$ column. 
The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
Zoom size 1 means we aggregate every point, which was in range of 100x100*0.000001 into one pixel. 
In zoom size N we aggregated NxN pixel from zoom size 1 into a new pixel.
%
For our measurements we specified the following data series:
\begin{itemize}
 \item The weight matrix W is from 3 to 43 with a stepsize of 4.
 \item The focal matrix F is from  17 to 125 with a stepsize of 12.
 \item The zoom level is from 1 to 5 with a stepsize of 1.
\end{itemize}
Therefore we calculate around 10*10*5=500 results for each fixed x.
The following conditions must hold F>W, F<Raster.cols und F<Raster.rows.

@@

\subsection{Heatmap}
\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{FocalRelation}
    \includegraphics[width=\linewidth]{images/FocalRealationUp}
    \label{fig:FocalRelation}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{WeightRealtion}
    \includegraphics[width=\linewidth]{images/WeightRelationUp}
    \label{fig:WeightRealtion}
  \end{subfigure}
  \caption{Heatmap of Relation between size of weight matrix $W$ and focal matrix $F$}
  \label{fig:RealtionUp}
\end{figure}

@@

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{FocalRelation}
    \includegraphics[width=\linewidth]{images/FocalRealationDown}
    \label{fig:FocalRelation}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{WeightRealtion}
    \includegraphics[width=\linewidth]{images/WeightRelationDown}
    \label{fig:WeightRealtion}
  \end{subfigure}
  \caption{Heatmap of Relation between size of weight matrix $W$ and focal matrix $F$}
  \label{fig:RealtionDown}
\end{figure}
\subsection{Clumping}

@@

% Focal size  
%	Increase of focal size leads to better results in the upward property
% 	Standard deviation decrease with higher focal size 
%	No standard deviation af F 17x17 because of missing clusters
%	The downward property reaches its maximum at 65x65
%
%	Conclusion: F should be around 65x65 or higher
In figure ~\ref{TODO Up} you can see that an increase of the focal size leads to better results for $SoH^{\uparrow}$. 
The standard deviation decreases also with a higher focal size. Only 
at focal size F of 17x17 there is no standard deviation. At focal size F 17x17 the standard deviation is 
missing, because the weight size W must be smaller than F. When F and W have similar
size, there are no clusters. (TODO assumtion for SOH, if no clusters we asume Up/Down = 0)
$SoH^{\downarrow}$ in figure ~\ref{TODO Down} reaches its maximum for focal size F 65x65 in the regarded area.
%
% Weight size
%	Increase of weight leads to increase of downward property
%	Small break downs for G* for upward and downward property
%	For the upward property Focal G* is better than G*
%
%	Conclusion: Higher weight size leads to better results. There are parametrisations of Focal G* which are better than G*
In figure ~\ref{TODO wDown} one can see that an increase of the weight size leads to better results.
Focal $G^*$ is not allways better than $G^*$ which would be a perfect result we hoped for. But it seems 
that $G*$ has at 23 and 39 some parametrisation which leads to small break downs. 
The standard deviation is in this area higher than in the other points.
In figure ~\ref{TODO wUp} the break downs are also visible.
The high standard deviation indicates that it is possible to use this parametrisation for better results
The $SoH^{\uparrow}$ in ~\ref{TODO wUp} is mostly better than $G^*$ which was our conclusion in \ref{TODO last paper}.
%
% Zoom
%	G* alwas better than Focal G* for upward and downward property
%	Focal G* has different focal sizes because zoom is compared
%	At zoom level 4 G* increase much more than Focal G*
%
%	Conclusion: G* is better than Focal G* in the zoom dimension, but the focal size is fixed. The zoom dimension has the least 
%	influence on the value
The last variation we examined was the zoom level. One can see that $G^*$ is always better than Focal $G^*$.
The target area of Focal $G^*$ increases if you zoom out.

\section{Conclusions and Future Work} \label{sec:Conclusion}

In this work, we generalized the Getis-Ord statistic to deal with the problem of
stability inherent in hot spot analysis. We identified possible underlying
reasons for this instability: The weight matrix as well as the size of the study
area. We developed a modified approach that deals with those two factors. The
result is a modified $G^*$ statistic called the \emph{Focal $G^*$ statistic}. It
reduces the study area used for comparison into regions and achieves through
this an increase in stability. To determine the effectiveness of our approach,
we propose a stability metric for hot spots called \emph{SoH}. To our knowledge
no such metric existed before this work. The SoH computes the ratio of
dependence of hot spots for different parametrizations of weight matrices. It
enables to express the stability between each parametrization using single value
restricted between zero and one. Based on this number one can decide which
parametrization to use and researchers can compare the stability of their
methods for unsupervised hot spot analyses. In particular, for temperature
values one wishes to detect those areas which have high differences regardless
of a particular parametrization. If a hot spot only appears for one
parametrization, the information gained for general use is quite small and can
even lead to an inefficient allocation of resources.

This research has several restrictions which have to be taken into account.
First, we only tested the $SoH^\uparrow$ metric. While we assume, based on our
graphical analysis, that the  $SoH^\downarrow$ stability should be similar, we
have no hard results. The results themselves are tested on two events in time
for a fixed area of the city of Karlsruhe. We have not tested it on smaller or
larger study areas, but we assume that the stability of the Focal $G^*$ would
stay the same whereas the stability of the $G^*$ statistic would increase with a
smaller study area and decrease with a larger study area. This follows the
reasoning that the impact of a singular point increases with a decrease of the
study area. To test this dependency is an interesting task for future work. The
last restriction is the fixed size in this work of the focal matrix for the
Focal $G^*$ approach. We only tested one size in this work, but it is highly
probable that the size of the focal matrix has an impact on the stability as
could be seen in Fig.~\ref{fig:EvalResults}. While an overall trend can be seen
in this work when the size of the weight matrix W and the focal matrix F are
almost identical, the exact ratio is beyond the scope of this work. The optimal
ratio as well as when the stability suffers from a too similar size are
interesting question for future work.

>>>>

Our results are based on the cab taxi data set from New York, Manhattan \cite{TODO}. 
We used only the dataset of January 2016. From that
dataset we used the $pickup\_longitude$ and $pickup\_latitude$ column. 
The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
Zoom size 1 means we aggregate every point, which was in range of 100x100*0.000001 into one pixel. 
In zoom size N we aggregated NxN pixel from zoom size 1 into a new pixel.
%
For our measurements we specified the following data series:
\begin{itemize}
 \item The weight matrix W is from 3 to 43 with a stepsize of 4.
 \item The focal matrix F is from  17 to 125 with a stepsize of 12.
 \item The zoom level is from 1 to 5 with a stepsize of 1.
\end{itemize}
Therefore we calculate around 10*10*5=500 results for each fixed x.
The following conditions must hold F>W, F<Raster.cols und F<Raster.rows.

@@

@@

\subsection{Clumping}

@@

% Focal size  
%	Increase of focal size leads to better results in the upward property
% 	Standard deviation decrease with higher focal size 
%	No standard deviation af F 17x17 because of missing clusters
%	The downward property reaches its maximum at 65x65
%
%	Conclusion: F should be around 65x65 or higher
In figure ~\ref{fig:fUp} you can see that an increase of the focal size leads to better results for $SoH^{\uparrow}$. 
The standard deviation decreases also with a higher focal size. Only 
at focal size F of 17x17 there is no standard deviation. At focal size F 17x17 the standard deviation is 
missing, because the weight size W must be smaller than F. When F and W have similar
size, there are no clusters. (TODO assumtion for SOH, if no clusters we asume Up/Down = 0)
$SoH^{\downarrow}$ in figure ~\ref{fig:fDown} reaches its maximum for focal size F 65x65 in the regarded area.

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for focal size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/fUp}
    \label{fig:fUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for focal size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/fDown}
    \label{fig:fDown}
  \end{subfigure}
  \caption{SoH for focal size}
  \label{fig:SoHFocal}
\end{figure}

%
% Weight size
%	Increase of weight leads to increase of downward property
%	Small break downs for G* for upward and downward property
%	For the upward property Focal G* is better than G*
%
%	Conclusion: Higher weight size leads to better results. There are parametrisations of Focal G* which are better than G*
In figure ~\ref{fig:wDown} one can see that an increase of the weight size leads to better results.
Focal $G^*$ is not allways better than $G^*$ which would be a perfect result we hoped for. But it seems 
that $G*$ has at 23 and 39 some parametrisation which leads to small break downs. 
The standard deviation is in this area higher than in the other points.
In figure ~\ref{fig:wUp} the break downs are also visible.
The high standard deviation indicates that it is possible to use this parametrisation for better results
The $SoH^{\uparrow}$ in ~\ref{fig:wUp} is mostly better than $G^*$ which was our conclusion in \ref{TODO last paper}.

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for weight size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/wUp}
    \label{fig:wUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for weight size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/wDown}
    \label{fig:wDown}
  \end{subfigure}
  \caption{SoH for weight size}
  \label{fig:SoHWeight}
\end{figure}
%
% Zoom
%	G* alwas better than Focal G* for upward and downward property
%	Focal G* has different focal sizes because zoom is compared
%	At zoom level 4 G* increase much more than Focal G*
%
%	Conclusion: G* is better than Focal G* in the zoom dimension, but the focal size is fixed. The zoom dimension has the least 
%	influence on the value
The last variation we examined was the zoom level. The results can seen in figure ~\ref{fig:SoHZoom}. One can see that $G^*$ is always better than Focal $G^*$.
The target area of Focal $G^*$ increases with every zoom step.

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for focal size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/zUp}
    \label{fig:zUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for focal size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/zDown}
    \label{fig:zDown}
  \end{subfigure}
  \caption{SoH for focal size}
  \label{fig:SoHZoom}
\end{figure}

\section{Conclusions and Future Work} \label{sec:Conclusion}
In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic on a different dataset.
We examined further parameters and evaluated that $G^*$ and Focal $G^*$ performe better if the weight
is higher.
Our results indicate a high Focal range for the upward property and a maximum of 65x65 for the downward property.
Therefore F should be not less than 65x65. 
If we calculate the SoH for the zoom level, Getis-Ord leads to better results. In general the zoom level 
has the least influence if $G^*$ or Focal $G^*$ performe better.
We assume that if Focal $G^*$ has a different Focal size for a different zoom level, it performes better, but this is beyond the
scope of this work.

With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
All our results are based on the SoH. Further work should validate or improve this metric and compare if
Focal $G^*$ can have better results than $G^*$ in all dimension with fixed weight and focal size.
